Reassessing the Impact of Dynamic Slicing in SFL

### 2019-02-08 paper/ijcai/paper.tex
pass sec 2 and sec 3 - small fixes

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool~\cite{lithium}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search
looking for chunks to remove from the file that satisfy the
oracle. When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere~\cite{lithium-complexity}. Our implementation is publicly
available.

@@

Intuitively, slicing enables identification of cells in the spectra
whose values can be set to zero, \ie{}, the components marked with 0
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one can observe that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
suspiciosness of those components decrease. Similar argument applies
to other fault predictors. In the example from
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.

>>>>

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool~\cite{lithium}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking 
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed. 
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere~\cite{lithium-complexity}. Our implementation is publicly
available.

@@

Intuitively, slicing enables identification of cells in the spectra
whose values can be set to zero, \ie{}, the components marked with 0
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one can observe that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
suspiciousness of those components decrease. Similar argument applies
to other fault predictors. In the example from
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.
